\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-12 manuscript/manuscript.tex
new microsoft data
addressed few problems in manuscript

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows.
\jy{Whrere is the 'block' part?}
\mc{addressed}
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}

@@

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as
it ...
The autocorrelation $\phi$ of the series was set to \{-0.9238795, -0.7071068, 
-0.3826834, 0, 0.3826834, 0.7071068, 0.9238795\}.
\mc{my explanation needs work}

>>>>

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\jy{Whrere is the 'block' part?}
\mc{addressed}
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

@@

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as
it ...
The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
-0.383, 0, 0.383, 0.707, 0.924\}. These
are the autocorrelations of the normal series, but after the transformation
to the marginal gamma distribution
\mc{my explanation needs work}
